Mapping parishe emissions: Framlingham as an example

### 2021-09-13 mappingParishes.Rmd
amended text & comments, reduced spurious feedback

Build a simple map just to check (Figure \@ref(fig:simpleParishMap).

@@

st_coord_sys <- sf::st_crs(parish_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

@@

Build a simple map from LSOAs based on the Framlingham electoral ward just to check (Figure \@ref(fig:simpleLSOAMap).

@@

st_coord_sys <- sf::st_crs(fram_lsoa_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

@@

Commercial gas & electricity use is at MSOA level. This may exceed the parish boundaries - find E02006288 (see above) and map it.

@@

st_coord_sys <- sf::st_crs(fram_msoa_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

@@

Yep, way too big.

This means we can only get residential electricity & gas at LSOA level and aggregate, all other data is at MSOA or LA level. See CREDS carbon.place for LSOA emissions estimates or CSE's impact tool for parish/LA emissions - both of these use the LSOA data for 2018/19 as part of their inputs.

>>>>

Build a simple map just to check the size of the parish (Figure \@ref(fig:simpleParishMap).

@@

st_coord_sys <- sf::st_crs(parish_sf_data) # check coord system
#st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

@@

Npw build a simple map from LSOAs based on the Framlingham electoral ward to see how well it matches the parish (Figure \@ref(fig:simpleLSOAMap).

@@

st_coord_sys <- sf::st_crs(fram_lsoa_sf_data) # check coord system
#st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

@@

Commercial gas & electricity use is at MSOA level. This may exceed the parish boundaries - find E02006288 (see above) and map it - Figure \@ref(fig:simpleMSOAMap).

@@

st_coord_sys <- sf::st_crs(fram_msoa_sf_data) # check coord system
#st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

@@

Yep, way too big. In fact this looks much like the [Framlingham electoral ward](https://www.suffolk.gov.uk/assets/council-and-democracy/how-the-council-works/SCC-Electoral-Division-Ward-Parish-map.pdf)...

This means we can only get residential electricity & gas at LSOA level and aggregate, all other data is at MSOA or LA level. See CREDS [carbon.place](https://www.carbon.place/) for LSOA emissions estimates or CSE's impact tool for parish/LA emissions - both of these use the LSOA data for 2018/19 as part of their inputs.
